---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
## Loading and preprocessing the data
Show any code that is needed to.

1. Load the data.
```{r,echo=FALSE}
#setwd("/media/caraya/DATA/CURSOS/02-Datascience/Reproducible_Research/RepData_PeerAssessment1")
#getwd()
#dir()
##----------------------------------------------------------------------------
```
```{r}
da<-read.csv("activity.csv")
```

2. Process/transform the data (if necessary) into a format suitable for your analysis
```{r}
library(ggplot2)
da$date<-as.Date(da$date)
datime<-as.POSIXlt(da$date)
```

## What is mean total number of steps taken per day?
1. Calculate the total number of steps taken per day.

The mean total number of steps taken per day is:
```{r}
mean(with(da, tapply(steps, date, sum)),na.rm=T)
```

2. If you do not understand the difference between a histogram and a barplot, research the difference between them. Make a histogram of the total number of steps taken each day.

```{r histograma,fig.height=4}
hist(with(da, tapply(steps, date, sum))
     ,main="Histogram: Total number of steps taken each day"
     ,xlab="Number of Steps"
     ,col="gray"
     ,breaks=8)
```

3. Calculate and report the mean and median of the total number of steps taken per day.

```{r}
summary(with(da, tapply(steps, date, sum)))
```

## What is the average daily activity pattern?

1. Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r}
y<-with(da, tapply(steps, date, mean))
x<-with(da, tapply(date, date, max))
x<-as.POSIXlt(names(x))
##plot(x,y,main="Daily Activity Pattern",type="l",xlab="date",ylab="steps")
qplot(x,y)
```

## Imputing missing values
If we imput missing values the mean of the values is NA:
```{r}
mean(with(da, tapply(steps, date, sum)),na.rm=F)
```

## Are there differences in activity patterns between weekdays and weekends?
For that, we do:
* Extract the week's days.
```{r}
wd<-weekdays(da$date)
```


